Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-03-02 article-models-tt.tex
cleaning up the commets in pretty type theory

Thus we make eight kinds of judgments in our type theory: ``$\Gamma$ is a context'',
``$A(i)$ is a family of contexts over $\Gamma$'', ``$A$ is a type in context $\Gamma$''
and ``$x$ is a term of the family $A$ of contexts over $\Gamma$''. The other four
judgments are for judgmental equality.

@@

@@

\subsection{The basic rules for judgmental equality}
The rules for judgmental equality establish that it is an equivalence relation
in all three cases (contexts, types and terms).
\bgroup\small
\begin{align*}
& \inference{\jvctx{\Gamma}}{\jvctxeq{\Gamma}{\Gamma}} 
& & \inference{\jvctxeq{\Gamma}{\Delta}}{\jvctxeq{\Delta}{\Gamma}} 
& & \inference{\jvctxeq{\Gamma}{\Delta}\qquad\jvctxeq{\Delta}{\greek{E}}}{\jvctxeq{\Gamma}{\greek{E}}}\\
& \inference{\jvfam{i}{\Gamma}{A}}{\jvfameq{i}{\Gamma}{A}{A}} 
& & \inference{\jvfameq{i}{\Gamma}{A}{B}}{\jvfameq{i}{\Gamma}{B}{A}}
& & \inference{\jvfameq{i}{\Gamma}{A}{B}\qquad\jvfameq{i}{\Gamma}{B}{C}}{\jvfameq{i}{\Gamma}{A}{C}}\\
& \inference{\jvterm{i}{\Gamma}{A}{x}}{\jvtermeq{i}{\Gamma}{A}{x}{x}}
& & \inference{\jvtermeq{i}{\Gamma}{A}{x}{y}}{\jvtermeq{i}{\Gamma}{A}{y}{x}}
& & \inference{\jvtermeq{i}{\Gamma}{A}{x}{y}\qquad\jvtermeq{i}{\Gamma}{A}{y}{z}}{\jvtermeq{i}{\Gamma}{A}{x}{z}}
\end{align*}
\egroup

@@

>>>>

\subsection{The basic judgments}
The basic judgments of pretty type theory are the same as for structural type
theory. There are judgments for: ``$\Gamma$ is a context'',
``$A(i)$ over $i:\Gamma$ is a family over $\Gamma$'', ``$A(i)$ over $i:\Gamma$ 
is a type in context $\Gamma$''
and ``$x(i)$ is a term of $A(i)$ above $i:\Gamma$''. The other four
judgments are for judgmental equality.

@@

We have the following basic inference rules that relate types and families:

@@

\subsection{The basic rules for judgmental equality}
The rules for judgmental equality establish that it is an equivalence relation.
\bgroup\small
\begin{align*}
& \inference{\jvctx{\Gamma}}{\jvctxeq{\Gamma}{\Gamma}} 
& & \inference{\jvctxeq{\Gamma}{\Delta}}{\jvctxeq{\Delta}{\Gamma}} 
& & \inference{\jvctxeq{\Gamma}{\Delta}\qquad\jvctxeq{\Delta}{\greek{E}}}{\jvctxeq{\Gamma}{\greek{E}}}\\
& \inference{\jvfam{i}{\Gamma}{A}}{\jvfameq{i}{\Gamma}{A}{A}} 
& & \inference{\jvfameq{i}{\Gamma}{A}{B}}{\jvfameq{i}{\Gamma}{B}{A}}
& & \inference{\jvfameq{i}{\Gamma}{A}{B}\qquad\jvfameq{i}{\Gamma}{B}{C}}{\jvfameq{i}{\Gamma}{A}{C}}\\
& \inference{\jvterm{i}{\Gamma}{A}{x}}{\jvtermeq{i}{\Gamma}{A}{x}{x}}
& & \inference{\jvtermeq{i}{\Gamma}{A}{x}{y}}{\jvtermeq{i}{\Gamma}{A}{y}{x}}
& & \inference{\jvtermeq{i}{\Gamma}{A}{x}{y}\qquad\jvtermeq{i}{\Gamma}{A}{y}{z}}{\jvtermeq{i}{\Gamma}{A}{x}{z}}
\end{align*}
\egroup

@@

\subsection{The empty context}
The empty context looks a bit strange when we explicitly denote the terms. But
we will not do so anymore after this subsection.
